\documentclass{common}

\cfoot{\color{gray} The MD5 of this file is \{\{TBD\}\}.}

\begin{document}

\name{Zhihao Shen}
\basicInfo{
    \email{\underline{i@shzh.me}} |
    \homepage[\underline{shzh.wiki}]{https://shzh.wiki} |
    \github[\underline{Sh-Zh-7}]{https://github.com/Sh-Zh-7} |
    \linkedin[\underline{LinkedIn}]{https://www.linkedin.com/in/imshzh7/}
}

\section{\faGraduationCap\ education}
\educationsubsection
    {Wuhan University (WHU)}{GPA: 3.67/4.0}{2018 -- Present}
    {\textit{Undergraduate student} in Computer Science (CS), expected June 2022}{Wuhan, China}

\section{\faCubes\ projects}
\projectsubsection
    {\textbf{sznn}}
    {https://github.com/ShZh-libraries/sznn}{0}
    {Jan. 2022 -- Apr. 2022}
\role{Rust/Typescript, Maintainer}{Graduation Projects}
High performance nerual network inference framework running on Web.
\begin{itemize}
    \item Pure JS backend is supported.
    \item Accelerate with WASM SIMD and multithread.
    \item Using WebGPU to significantly improve the throughput.
\end{itemize}
\projectsubsection
    {\textbf{ShZh Playground}}
    {https://github.com/ShZh-Playground}{3}
    {Aug. 2020 -- Present}
\role{C++/Rust/Java .etc, Maintainer}{Individual Projects}
Collections of my tools and wheels. Update from time to time.
\begin{itemize}
    \item Tiny MIPS CPU and tiny-OS are undergraduate courses' requirements.
    \item DB, compilers and other projects are made for fun in spare time.
    \item High level projects like react-like library are also included.
\end{itemize}
\projectsubsection
    {\textbf{ShZh Websites}}
    {https://github.com/ShZh-websites}{0}
    {Sep. 2021 -- Present}
\role{Svelte/ReScript/Tex, Maintainer}{Individual Projects}
Collections of my websites, including my personal homepage, blogs, diaries and so on.
\begin{itemize}
    \item Modern web technologies such as Tailwind, Alpline and Gatsby are used.
    \item Highly optimized for user experience, Lighthouse score guaranteed.
    \item Flexible, responsive design. Not only works in mobile, but also works in dark mode.
\end{itemize}

\section{\faTrophy\ awards}
\award
    {\textbf{- China Software Cup}, \nth{3} Prize, \textit{Captain}}{Oct. 2020}
    {Intelligent applications for traffic scenes based on computer vision. 
        {\href{https://github.com/Sh-Zh-7/intelligent-transportation-system}{\underline{\faGithub}} \faStarO\ 26}
    }
\award
    {\textbf{- APMCM}, \nth{2} Prize}{Nov. 2019}
    {Analysis and decision-making of regional economic vitality and its influencing factors.}

\section{\faCogs\ skills}
\begin{itemize}[parsep=0.5ex]
    \item \textbf{AI}: Machine Learning, Reinforce Learning
    \item \textbf{HPC}: C/C++/Rust, ARM/x86 SIMD, OpenMP, CUDA, MPI
    \item \textbf{DB}: MySQL, Redis/memcached, boltDB, levelDB, DuckDB, .etc.
    \item \textbf{Web Backend}: Java/Go/Kotlin, Sprint Boot/Spring Cloud, .etc.
    \item \textbf{Web Frontend}: H5/C3, JS/WASM, TypeScript/ReScript, Vue/React/Angular/Svelte
\end{itemize}

\section{\faInfo\ miscellaneous}
\begin{itemize}[parsep=0.5ex]
    \item \textbf{Mandarin}: Native speaker
    \item \textbf{English}: CET-6: 463 | CET-4: 556
    \item \textbf{Linktree}: \href{https://linktr.ee/ShZh7}{\underline{https://linktr.ee/ShZh7}}
\end{itemize}

\end{document}